%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Lachaise Assignment
% LaTeX Template
% Version 1.0 (26/6/2018)
%
% This template originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Marion Lachaise & François Févotte
% Vel (vel@LaTeXTemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{article}

\input{structure.tex} % Include the file specifying the document structure and custom commands

%----------------------------------------------------------------------------------------
%	ASSIGNMENT INFORMATION
%----------------------------------------------------------------------------------------

\title{Fourier Analysis Stein: Chapter 7. Problems.} % Title of the assignment

\author{Kelvin Hong\\ \texttt{kh.boon2@gmail.com}} % Author name and email address

\date{Xiamen University Malaysia, Asia Pacific University Malaysia --- \today} % University, school and/or department name(s) and a date

%----------------------------------------------------------------------------------------

\begin{document}

\maketitle % Print the title

\section{Problems}

\begin{enumerate}
    \item Let $f$ be a function on the circle. For each $N\geq 1$ the discrete Fourier coefficients of $f$ are defined by
    $$a_N(n) = \dfrac1N \sum_{k=1}^N f(e^{2\pi ik/N}) e^{-2\pi ikn/N}, \qquad \text{ for } n\in\mathbb Z.$$
    We also let 
    $$a(n) = \int_0^1 f(e^{2\pi ix}) e^{-2\pi nx} dx$$
    denote the ordinary Fourier coefficients of $f$. 
    \begin{enumerate}[(a)]
        \item Show that $a_N(n) = a_N(n+N)$.
        
        \begin{solution}
            The only term related to $n$ is $e^{-2\pi ikn/N}$, so it is trivial to see this term is periodic with a period of $N$.
        \end{solution}

        \item Prove that if $f$ is continuous, then $a_N(n)\to a(n)$ as $N\to\infty$.
        
        \begin{solution}
            Let $n$ be a fixed integer. Since $f$ is continuous and periodic, it is bounded, we assume it is bounded above by a constant $M>0$.
            Given $\varepsilon>0$, we may choose a large enough $N$ such that 
            $$|e^{-2\pi inx} - e^{-2\pi iny}| < \dfrac\varepsilon{2M} \text{ whenever } |x-y|<\dfrac1N.$$
            Also, $f$ is uniformly continuous because it is periodic, so we may choose another large enough $N'$ so that
            $$|f(e^{2\pi i x}) - f(e^{2\pi i y})| < \dfrac\varepsilon2 \text{ whenever } |x-y|<\dfrac1{N'}.$$
            We now simply choose $N_0=\max(N, N')$ so the above two can be satisfied.

            For $N>N_0$ we have
            \begin{align*}
                |a_N(n) - a(n)| &= \abs{
                        \sum_{k=1}^N \left[\dfrac1N f(e^{2\pi ik/N}) e^{-2\pi ikn/N} - 
                        \int_{(k-1)/N}^{k/N} f(e^{2\pi ix}) e^{-2\pi inx}dx\right]
                    } \\
                    &\leq \sum_{k=1}^N \int_{(k-1)/N}^{k/N} \abs{
                        f(e^{2\pi ik/N}) e^{-2\pi ikn/N} - f(e^{2\pi ix})e^{-2\pi inx}
                    }dx.
            \end{align*}

            The inner term can be estimated like so:
            \begin{align*}
                &\abs{
                    f(e^{2\pi ik/N}) e^{-2\pi ikn/N} - f(e^{2\pi ix})e^{-2\pi inx}
                } \\
                \leq &\abs{
                    f(e^{2\pi ik/N}) - f(e^{2\pi ix})
                } + \abs{ f(e^{2\pi ix}) } \abs{
                    e^{-2\pi ikn/N} - e^{-2\pi inx}
                }\\
                < &\varepsilon.
            \end{align*}
            This proves $\lim_{N\to\infty}a_N(n)=a(n)$.
        \end{solution}
    \end{enumerate}
    
    \item If $f$ is a $C^1$ function on the circle, prove that $\abs{a_N(n)} \leq c/\abs{n}$ whenever $0<\abs{n}\leq N/2$.

    \begin{solution}
        We have to clarify that $c$ will be a constant that is independent from $n$ and $N$, possible related only to $f$.
        We also only prove the statement for $0<n\leq N/2$, i.e., positive $n$, the proof for negative $n$ should be nearly identical.

        Since $f$ is periodic and $C^1$, it is Lipchitz continuous. 
        \href{https://math.stackexchange.com/questions/4353734/if-f-is-periodic-and-c1-class-then-lipschitz-continuous}{See this answer.}
        Therefore, we let $M$ be a positive constant such that
        $$\abs{f(x)-f(y)} \leq M \abs{x-y} \quad \text{ for all }x,y \text{ on the circle.}$$

        We also use the identity: $|1-e^{i\theta}|=2\sin(\theta/2)\leq \theta$ for $\theta\in[0,\pi]$.

        Following the hint from the book, we let $\ell=1$ if $N/4< n\leq N/2$. If otherwise $n\leq N/4$, we let $\ell$ be the
        largest integer satisfying $\ell n/N\leq 1/2$, then since $(\ell+1)n/N>1/2$, we have 
        $$\abs{\frac12 - \dfrac{\ell n}{N}} = \frac12 - \dfrac{\ell n}{N} < \dfrac nN \leq \frac14.$$
        This is to verify that we can always choose $\ell$ such that $1/4 \leq \ell n/N \leq 1/2$ by construction, and that we also have
        the following lower bound:
        $$\dfrac{\pi}{2} \leq \dfrac{2\pi \ell n}{N} \leq \pi \implies \abs{1-e^{2\pi i\ell n/N}}\geq \sqrt2.$$

        Everything is ready, we now have
        \begin{align*}
            \abs{a_N(n)} \sqrt2 &\leq \abs{a_N(n)} \abs{1-e^{2\pi i\ell n/N}}\\
            &\leq \frac1N \sum_{k=1}^N M\abs{1-e^{2\pi i\ell/N}}\\
            &=  M\abs{1-e^{2\pi i\ell/N}}\\
            &\leq M\cdot \dfrac{2\pi \ell}N\\
            \therefore \abs{a_N(n)}&\leq \dfrac{M\pi}{\sqrt2 n}.
        \end{align*}
    \end{solution}

    \item By a similar method, show that if $f$ is a $C^2$ function on the circle, then
    $$\abs{a_N(n)} \leq c/\abs{n}^2, \quad \text{whenever } 0< \abs{n} \leq N/2.$$

    As a result, prove the inversion formula for $f\in C^2$,
    $$f(e^{2\pi ix}) = \sum_{n=-\infty}^\infty a(n) e^{2\pi inx}$$
    from its finite version.

    \begin{solution}
        We use the second symmetric difference and the fact that $f''$ is bounded above, that 
        $$\abs{f(e^{2\pi i(k+\ell)/N}) - 2f(e^{2\pi ik/N}) + f(e^{2\pi i(k-\ell)/N})} \leq \dfrac{M\ell^2}{N^2}.$$
        
        For me, I can't overcome the fact that how to apply the mean value theorem on complex domain, so I just simply let
        $g: [0,1]\to \mathbb R$ such that $g(x) = f(e^{2\pi ix})$, then it follows that $g$ is a real-valued, periodic $C^2$ function
        on $[0,1]$. This translate to the bound above.

        By this logic and choosing a suitable integer $\ell$ as in previous solution, we find ourselves at
        \begin{align*}
            a_N(n)\left(1-e^{2\pi i\ell n/N}\right)^2 e^{-2\pi i\ell n/N} &= \dfrac{1}{N} \sum_{k=1}^N \\
                &\left[f(e^{2\pi i(k+\ell)/N}-2f(e^{2\pi ik/N})+f(e^{2\pi i(k-\ell)/N})) e^{-2\pi ikn/N}\right]\\
            \abs{a_N(n)} \abs{1-e^{2\pi i\ell n/N}}^2 &\leq \dfrac1N \sum_{k=1}^N \dfrac{M\ell^2}{N^2}\\
            &\leq \dfrac{M\ell^2}{N^2}.
        \end{align*}
        Since $\ell/N\leq 1/(2n)$ and $\abs{1-e^{2\pi i\ell n/N}}\geq \sqrt2$, we manage to show that
        $$\abs{a_N(n)}\leq \dfrac M{8n^2}.$$

        (Second part no solution for now.)
    \end{solution}

    \item Let $e$ be a character on $G=\mathbb Z(N)$, the additive group of integers modulo $N$. Show that there exists a unique
    $0\leq \ell\leq N-1$ so that 
    $$e(k) = e_\ell(k) = e^{2\pi i\ell k/N}\quad\text{ for all } k\in\mathbb Z(N).$$

    Conversely, every function of this type is a character on $\mathbb Z(N)$. Deduce that $e_\ell\mapsto \ell$ defines an
    isomorphism from $G$ to $G$.

    \begin{solution}
        Let $e: G\to S^1$ be a character, if it is an identity character, then $e=e_0$.
        If $e$ is non-trivial, then we let $a\in G$ so that $e(a)\neq 1$.
        Since $n\cdot a$ is the identity element in $G$, we have that 
        $$e(a)^n = e(n\cdot a) = 1.$$
        This shows that $e(a)$ is a root of unity, and thus there is a unique $0\leq \ell< N$ such that $e=e_\ell$.

        To show the mapping $M: \hat G \to G$ defined by $M(e_\ell) = \ell$ is an isomorphism, it is worth noting this is a
        well-defined mapping, i.e., for $\ell, k\in \mathbb Z(N)$, $M(e_\ell)=M(e_k)$ implies $\ell=k$.
        Moreover, this mapping is surjective and one-to-one, we only have to show it is a homomorphism:
        $$M(e_\ell \circ e_k) = M(e_{\ell+k}) = \ell+k\pmod N.$$
    \end{solution}

    \item Show that all characters on $S^1$ are given by 
    $$e_n(x) = e^{2\pi inx}\text{ with }n\in \mathbb Z,$$
    and check that $e_n\mapsto n$ defines an isomorphism from $\widehat{S^1}$ to $\mathbb Z$. 

    \begin{solution}
        To make the discussion less confusing, we will use $f$ to denote a character on $S^1$, which is $f: S^1\to S^1$.

        We can then define $F: \mathbb R\to S^1$ so that $F(x) = f(e^{2\pi ix})$, it is not hard to see $F$ is a periodic function
        with a period of $1$, and also satisfying $F(x+y) = F(x)F(y)$.

        Clearly $F$ is a complex-valued continuous function, with $F(0)=1$, hence there is a small enough $\delta>0$ such that
        $c=\int_0^\delta F(y)dy\neq 0$. We then have
        \begin{align*}
            cF(x) &= \int_0^\delta F(x+y)dy\\
            &= \int_x^{x+\delta} F(y)dy\\
            \therefore cF'(x) &= F(x+\delta) - F(x)\\
            &= [F(\delta)-1]F(x)\\
            F'(x) &= \dfrac{F(\delta)-1}{c}F(x).
        \end{align*} 
        Thus, $F'(x) = AF(x)$ for some constant $A$, combine with the condition that $F(0)=1$, we have $F(x) = e^{Ax}$.

        Since $F(x)$ have values in $S^1$, $A=2\pi in$ for some real number $n$.

        To show that $n$ is an integer, we have $e^{2\pi in} = F(1)=f(e^{2\pi i}) = 1$, so $f(e^{2\pi ix})=e_n(x)$ for $x\in\mathbb R$.

        Clearly if $n\neq m$ are integers, then $e_n\neq e_m$, and for each integer $n$, $e_n$ is a character on $S^1$. We only have to show
        $L: \widehat{S^1} \to \mathbb Z$ is a homomorphism. For all $x\in\mathbb R$ we have $e_n\circ e_m(x) = e^{2\pi i(n+m)x}$,
        hence $L(e_n\circ e_m) = n+m = L(e_n) + L(e_m)$.
    \end{solution}

    \item Prove that all characters on $\mathbb R$ take the form
    $$e_\xi(x) = e^{2\pi i\xi x}\quad \text{ with }\xi\in\mathbb R.$$
    and that $e_\xi\mapsto \xi$ defines an isomorphism from $\widehat{\mathbb R}$ to $\mathbb R$. The argument in Exercise 5
    applies here as well.

    \begin{solution}
        We use $F$ to denote a character on $\mathbb R$, which is $F: \mathbb R\to S^1$. Since $\mathbb R$ is an additive group,
        we have $F(x+y) = F(x)F(y)$, and also $F(0)=1$.

        Using what we proved in the previous exercise, there is a constant $A$ such that $F(x) = e^{Ax}$, and since $F$ maps to norm of 1,
        $A=2\pi i\xi$ for some real number $\xi$.

        Now we see that for any real $\xi$, $F$ is a character on $\mathbb R$, and $F(x) = e_\xi(x)$.

        It is clear that the mapping $e_\xi\mapsto \xi$ is surjective and one-to-one, we only have to show it is a homomorphism by
        noting that $e_{\xi+\eta}(x) = e^{2\pi i(\xi+\eta)x} = e^{2\pi i\xi x}e^{2\pi i\eta x} = e_\xi(x)e_\eta(x)$ for any $\xi, \eta\in\mathbb R$.

    \end{solution}

    \item Let $\xi=e^{2\pi i/N}$. Define the $N\times N$ matrix $M=(a_{jk})_{1\leq j,k\leq N}$ by $a_{jk}=N^{-1/2}\xi^{jk}$.
    \begin{enumerate}
        \item Show that $M$ is unitary.
        
        \begin{solution}
            Write $M=\begin{bmatrix}
                \vec{a_1} | \cdots | \vec{a_N}
            \end{bmatrix}$ where each column vector is $\vec{a_k}=(a_{1k}\dots a_{Nk})^T$. Then we have that for $1\leq k,n\leq N$,
            $$\vec{a_k}^* \vec{a_n} = \dfrac1N \sum_{j=1}^N \overline{\xi^{jk}} \xi^{jn} = \dfrac1N \sum_{j=1}^N \xi^{j(n-k)} = \delta_{kn}.$$
            Where it means that $\delta_{kn}=1$ when $k=n$, and $\delta_{kn}=0$ otherwise. This proves $M$ to be a unitary matrix.
        \end{solution}

        \item Interpret the identity $(Mu, Mv) = (u,v)$ and the fact that $M^*=M^{-1}$ in terms of the Fourier series on $\mathbb Z(N)$.
        
        \begin{solution}
            Not too sure what is the point of the question here.
        \end{solution}
    \end{enumerate}

    \item Suppose that $P(x) = \sum_{n=1}^N a_ne^{2\pi i nx}$.
    \begin{enumerate}
        \item Show by using the Parseval identities for the circle and $\mathbb Z(N)$, that
        $$\int_0^1 \abs{P(x)}^2 dx = \dfrac1N \sum_{j=1}^N \abs{P(j/N)}^2.$$
        \begin{solution}
            Notice that $P$ looks like a function on $\mathbb R$, but essentially it is a function on $\mathbb Z(N)$.
            We let $e_n(x)=e^{2\pi inx}$ to be characters on $S^1$, then we find that $P=\sum_{n=1}^N a_n e_n$.
            Moreover, for $x\in\mathbb Z(N)$ which by that we means $x=0,1,\dots, N-1$, we let $F(x)=P(x/N)$, so $F$ is a function on $\mathbb Z(N)$.

            We note that we can define an inner product for periodic functions $f,g$ over $[0,1]$ on $\mathbb R$ as $(f,g)=\int_0^1 f\bar g$,
            then $\{e_n\}_{1\leq n\leq N}$ is orthonormal. We thus can have
            $$\int_0^1 \abs{P(x)}^2 dx = (P, P) = \sum_{j=1}^N \sum_{k=1}^N a_j\overline{a_k} (e_j, e_k) = \sum_{n=1}^N \abs{a_n}^2.$$

            Apply Parseval identity to $F$ and using the inner product for functions on $\mathbb Z(N)$, we have
            $$\sum_{n=1}^N \abs{a_n}^2 = (F,F) = \dfrac1N \sum_{x=1}^N  \abs{F(x)}^2 = \dfrac1N \sum_{x=1}^N \abs{P\left(\dfrac xN\right)}^2.$$
            This completes the proof.
        \end{solution}

        \item Prove the reconstruction formula
        $$P(x) = \sum_{j=1}^N P(j/N) K(x-(j/N))$$
        where 
        $$K(x) = \dfrac{e^{2\pi ix}}{N} \dfrac{1-e^{2\pi iNx}}{1-e^{2\pi ix}} = \dfrac1N (e^{2\pi ix} + e^{2\pi i2x} + \cdots + e^{2\pi iNx}).$$

        \begin{solution}
            For ease of notation, we let $e_k(x)=e^{2\pi ikx}$, and also $\xi=e^{2\pi i/N}$ to be the $N$-th root of unity. We have

            \begin{align}
                \text{RHS} &= \sum_{j=1}^N \sum_{n=1}^N a_n\xi^{nj} \cdot \dfrac1N \sum_{k=1}^N \dfrac{e_k(x)}{\xi^{kj}}\\
                &= \dfrac1N \sum_{n=1}^N\sum_{k=1}^N \left(\sum_{j=1}^N \xi^{(n-k)j}\right) a_ne_k(x)\\
                &= \sum_{n=1}^k a_n e_n(x) = P(x).
            \end{align}
        \end{solution}
    \end{enumerate}
    
    \item (This question was skipped)
    \item A group $G$ is \textbf{cyclic} if there exists $g\in G$ that generates all of $G$, that is, if any element in $G$ can be written
    as $g^n$ for some $n\in\mathbb Z$. Prove that a finite abelian group is cyclic if and only if it is isomorphic to $\mathbb Z(N)$
    for some $N$.

    \begin{solution}
        Let $G$ be a finite abelian group. Apparently if $G$ is isomorphic to $\mathbb Z(N)$ then it is cyclic, since it can be generated by
        the element that is isomorphic to $1\in\mathbb Z(N)$.
        Now assume $G$ is cyclic and let $g$ be the generator of $G$. Since $G$ is finite, there is a smallest positive integer $n$ such that
        $g^n=e$. We define the mapping $\varphi: \mathbb Z(n)\to G$ by $\varphi(k)=g^k$. This is a homomorphism because
        $\varphi(k+\ell)=\varphi(k)\varphi(\ell)$. It is also one-to-one and surjective, hence it is an isomorphism.
    \end{solution}

    \item (This question was also skipped :p)
    \item Suppose that $G$ is a finite abelian group and $e: G\to \mathbb C$ is a function that satisfies $e(x\cdot y) = e(x)e(y)$ for all
    $x,y\in G$. Prove that either $e$ is identically $0$, or $e$ never vanishes. In the second case, show that for each $x$, $e(x)=e^{2\pi ir}$
    for some $r\in\mathbb Q$  of the form $r=p/q$, where $q=|G|$. 

    \begin{solution}
        Let's assume the non-trivial that $e\not\equiv 0$, then we must have $e(1)\neq 0$, or else for every $f\in G$, $e(f)=e(1)e(f)=0$.
        Based on this we also have $e(1)=1$.
        Now for each element $g\in G$, we have $g^{|G|}=1\in G$, hence
        $e(g)^{|G|} =e(g^{|G|})=e(1)=1$. This not only show that $e(g)\neq 0$, but also that $e(g)$ is a $|G|$-th root of unity, which means
        we may write $e(g)=e^{2\pi ip/|G|}$ for some integer $p$.
    \end{solution}

    \item In analogy with ordinary Fourier series, one may interpret finite Fourier expansions using convolutions as follows.
    Suppose $G$ is a finite abelian group, $1_G$ its unit, and $V$ the vector space of complex-valued functions on $G$.

    \begin{enumerate}
        \item The convolution of two functions $f$ and $g$ in $V$ is defined for each $a\in G$ by
        $$(f * g)(a) = \dfrac1{\abs G} \sum_{b\in G} f(b) g(a\cdot b^{-1}).$$
        Show that for all $e\in \hat G$ one has $\widehat{(f*g)} (e) = \hat f(e) \hat g(e)$.
        
        \begin{solution}
            
        \end{solution}
    \end{enumerate}
\end{enumerate}



\end{document}
